### 2016-05-03 paper/paper.tex
add background, cleanup things

In this paper, we present DDoSCoin, which is a cryptocurrency with a
\emph{mallicious} proof-of-work. DDoSCoin allows miners to prove that they have
contributed to a distributed denial of service attack against a specific target.
This proof involves making a large number of TLS connections to a target server,
and using infrequent cryptographic responses as a proof.

@@

@@

Proof-of-Stake is an alternate way of generating new blocks in a cryptocurrency.
In this system, blocks are ``minted'' (rather than mined) based on how much
stake the miner has in the currency (rather than their fraction of computational
power). Proof-of-stake assumes that the underlying cryptocurrency is already
somewhat distributed, for example through the use of a traditional proof-of-work
system. In this subsection, we will describe Peercoin, a currently active
alternate cryptocurrency that employs a hybrid proof-of-work and proof-of-stake
algorithm to mint blocks.

@@

If DDoSCoin accepted proofs against any TLS 1.2 server, miners would be
incentivized to set up signed TLS servers locally, and focus exclusively on
solving those challenges instead of remote ones, leading to the
proof-of-work being a computational puzzle rather than one based on
participation in a network denial of service. Thus, DDoSCoin must have a way to
agree on what victims are acceptable targets for the proofs-of-work to be considered
valid. Similarly, it is important to focus the denial-of-service effort toward a
single or small number of victims in order to have the most impact.

One simple way to is to hardcode a set of victim certificates into the protocol.
For example, DDoSCoin's published code could contain the identities of
Facebook's servers, and only incentivize attacks against them. However, there
are many attackers that might feel uncomfortable attacking Facebook, but would
be willing to participate in attacks against other websites. In addition, having
only a single or small set of websites is a risk to DDoSCoin: if those websites
all go offline or successfully mitigate the attacks (such as by disabling TLS),
no future DDoSCoin blocks can be mined, and the currency will stall. At this
point, all DDoSCoins in circulation would become nearly worthless, as there
would be no way to safely transact them.

These issues lead to a few subtle requirements for choosing valid victims.
First, there must be \emph{limits} on who is allowed to be a victim, otherwise
miners can create local computational puzzles. At the same time, there must be
\emph{enough} targets in order to be robust against stalled blockchains.
Similarly, the list of victims must be \emph{flexible} in order to allow
removing targets as they become impractical to attack (either
through successful attack or mitigation), and adding new ones.

@@

In order to allow victims to be (temporarily) selected for DoS, DDoSCoin
allows ``bounties'' for targetting specific servers. To accomplish this,
DDoSCoin introduces a new payment opcode, PAY\_TO\_DDOS, that can be used in
transactions subject to certain constraints. This opcode takes two arguments in
the output script: a
string representing a domain name that the payer wishes to have DDoSed, and a
target difficulty. Once this transaction is stored in a valid block, anyone can
collect its reward by creating a connection to the specified victim server, with
a response that meets the given target difficulty. These connections are made
similar to the way that miners connect to victim servers to create blocks, but
with a few important differences. First, the \texttt{client\_random} is
generated using the PAY\_TO\_DDOS transaction ID (txid), the SHA256 hash of the
output script the payee wants to collect the payment with, and a random nonce.
The client then makes connections to the specified victim domain until its
response meets the target difficulty
(SHA256(\texttt{server\_key\_exchange\_params} || \texttt{signature} ||
\texttt{nonce}) < target).

@@

There are a couple important features of this transaction. First, the reason the
transaction ID of the PAY\_TO\_DDOS transaction is included (committed to) in
the \texttt{client\_random} is to prevent a client from ``double-claiming''
multiple bounty rewards with the same proof-of-DoS. Similarly, the client
commits to the (hash of the) output script of the claiming transaction to
prevent others from being able to swap it for their own, therby ``stealing'' the
proof-of-DoS and collect the reward themselves. These combined allow two
mutaully-distrusting parties to directly and safely transact currency in
exchange for a DoS attack.

@@

Proof-of-Stake to decide a delta on the victim-list.

-However, the victim could easily generate a new certificate; should instead
base identity off domain rooted to valid root CAs.

DDoSCoin must select a small set of victim servers to p

-Miners vote (proof-of-stake-esq)

>>>>

In this paper, we present DDoSCoin, which is a cryptocurrency with a
\emph{mallicious} proof-of-work. DDoSCoin allows miners to prove that they have
contributed to a distributed denial of service attack against specific target
servers.  This proof involves making a large number of TLS connections to a
target server, and using infrequent cryptographic responses to prove that a
large number of connections has been made. Like proof-of-work puzzles, these
proofs are inexpensive to verify, and can be made arbitrarily difficult to
solve.

@@

In this section, we review relevant basics of cryptocurrency. For a more
detail, we refer the reader to other
sources~\cite{bitcoin-book,bitcoin-paper,bitcoin-sok}.

\subsection{Cryptocurrency}

Bitcoin employs a hash-based proof-of-work protocol to construct a public ledger
of transactions. In this protocol, miners attempt to solve a simple hash-based
computational puzzle in order to mine blocks. Mining a block nets the miner a
reward, and the right to specify what new (valid) transactions should be
included in the public ledger. To mine a block, a miner must find a hash of a
block header that is less than an adjustable target. The block header includes
the hash of the last block found, the merkle root of the list of transactions
the miner wants to include in this block, and a nonce. The easiest way to solve
this puzzle is to iterate the nonce\footnote{or modify transactions, therby
changing the merkle root} until the hash satisfies the target difficulty. Then,
the miner publishes the found block, and miners use this block as the latest
block.

@@

Proof-of-Stake is an alternate way of generating new blocks in a cryptocurrency.
In this system, blocks are ``minted'' (rather than mined) based on how much
stake the miner has in the currency (rather than their fraction of computational
power). Proof-of-stake assumes that the underlying cryptocurrency is already
somewhat distributed, for example through the use of a traditional proof-of-work
system. In this subsection, we will describe Peercoin, an active
alternate cryptocurrency that employs a hybrid proof-of-work and proof-of-stake
algorithm to mint blocks. For more details on proof-of-stake, we refer the
reader to the Peercoin~\cite{peercoin} and NXT~\cite{nxt} whitepapers.

@@

If DDoSCoin accepted proofs against any TLS 1.2 server, miners would be
incentivized to set up their own TLS servers locally, and focus exclusively on
``attacking'' those servers instead of remote ones. Since the miner would have
access to the private key for that server, they would not be required to even
create network connections, leading to the proof-of-work being a computational
puzzle rather than one based on participation in a network denial of service.
To prevent this, DDoSCoin must have a way to agree on what victims are
acceptable targets for the proofs-of-work to be considered valid. Similarly, it
is important to focus the denial-of-service effort toward a single or small
number of victims in order to have the most impact.

One simple solution is to hardcode a set of victim certificates into the
protocol.  For example, DDoSCoin's published code could contain the identities
of Facebook's servers and domains, and only allow and incentivize attacks
against them. However, there are many attackers that might feel uncomfortable
attacking Facebook, but would be willing to participate in attacks against other
websites. In addition, having only a single or small set of victim websites is a
risk to DDoSCoin: if those websites all go offline or successfully mitigate the
attacks (such as by disabling TLS), no future DDoSCoin blocks can be mined, and
the currency will stall. At this point, all DDoSCoins in circulation would
become nearly worthless, as there would be no way to safely transact them.

These issues lead to a few subtle requirements for choosing valid victims.
First, there must be \emph{limits} on who is allowed to be a victim, otherwise
miners can create local computational puzzles. At the same time, there must be
\emph{enough} targets in order to be robust against stalled blockchains.
Similarly, the list of victims must be \emph{flexible} in order to allow
removing targets as they become impractical to attack (either
through successful attack or mitigation), and adding new ones to take their
place.

@@

In order to allow victims to be (temporarily) selected for DoS, DDoSCoin allows
``bounties'' for targetting specific servers. To accomplish this, DDoSCoin
introduces a new payment opcode, PAY\_TO\_DDOS, that can be used in transactions
subject to certain constraints. This opcode takes two arguments in an output
script: a string representing a domain name that the payer wishes to have
DDoSed, and a target difficulty corresponding to the amount of connections the
payer wishes to be made. Once this transaction is stored in a valid block,
anyone can collect its reward by creating a connection to the specified victim
server and obtaining a response that meets the given target difficulty. These
connections are made similar to the way that miners connect to victim servers to
create blocks, but with a few important differences. First, the
\texttt{client\_random} is generated using the PAY\_TO\_DDOS transaction ID
(txid), the SHA256 hash of the output script the payee wants to collect the
payment with, and a random nonce.  The client then makes connections to the
specified victim domain until it gets a response that meets the target
difficulty specified by the PAY\_TO\_DDOS transaction.
(SHA256(\texttt{server\_key\_exchange\_params} || \texttt{signature} ||
\texttt{nonce}) < target).

@@

There are a couple important features of this transaction. First, the reason the
transaction ID of the PAY\_TO\_DDOS transaction is included (committed to) in
the \texttt{client\_random} is to prevent a client from ``double-claiming''
multiple bounty rewards with the same proof-of-DoS. Similarly, the client
commits to (a hash of) the output script of the claiming transaction to
prevent others from being able to swap it for their own, therby ``stealing'' the
proof-of-DoS and collect the reward themselves. These properties combined allow two
mutaully-distrusting parties to directly and safely transact currency in
exchange for a specified-amount of work in a DoS attack.

% Maybe move this to discussion....
Since PAY\_TO\_DDOS transactions can be claimed by anyone, there is a risk to
the collector that by the time they complete their DoS attack, someone else will
have collected the payment. In addition, a potential victim website could
disincentivze attacks by submitting PAY\_TO\_DDOS transactions that they can
quickly solve locally. This would cause attackers to try to connect to them, and
eventually even collect a response that meets the target difficulty. However,
when the attacker went to publish this to collect the reward, the victim could
publish their proof, essentially double-spending the PAY\_TO\_DDOS transaction.
With some probability, the victim's transaction will ``win'' and prevent the
attacker from collecting the reward. Over the long term, attackers may be wary
of attacking such targets, and instead require higher payouts for attacking them
to cover such risks.

@@

In order to allow the victim list to be updated dynamically, DDoSCoin uses
\emph{Proof-of-Stake} to let currency holders make small changes to the list of
acceptable victim domains. Using proof-of-stake ensures that updates are only
done by actors that already have a substantial stake in the currency, either by
purchasing it or by previously participating in the (DoS) mining themselves.

To update the list, a currency holder ``mints'' a proof-of-stake transaction
similar to Peercoin. First, they must hold a number of coins that have been
unspent for more than 30 days. After the 30 days have passed, each second the
minter
hashes the aged transaction, a recent stake-modifier block, and a current
(seconds-resolution) timestamp. If this hash is less than the current
proof-of-stake target difficulty multiplied by the coin-age being consumed in
this transaction, then the currency holder is allowed to make a new
proof-of-stake block. Inside this block, the currency holder can make one
addition to (or one deletion from) the current victim list.

Proof-of-stake blocks contains no coinbase or coinstake reward, and transaction
fees are not collected. Thus, there is no direct short-term monetary incentive
to produce such a block. The intention is that this will encourage only those
with a vested interest in the long-term success of DDoSCoin to participate in
updating the victim list.

After this block has been published, miners must wait until 10 proof-of-DoS
(non-proof-of-stake) blocks have been mined before the specified delta to the
change list is applied. This discourages malicious miners from forking the chain
at an earlier block with a proof-of-stake block adding their local domain to the
victim list, and immediately mining blocks on top of it to catch up to the main
chain.

%Proof-of-Stake to decide a delta on the victim-list.

%-However, the victim could easily generate a new certificate; should instead
%base identity off domain rooted to valid root CAs.

%DDoSCoin must select a small set of victim servers to p

%-Miners vote (proof-of-stake-esq)
